---
title: "Recommendations and maps"
author: "Kori Blakenship and Randy Swaty"
date: "2022-03-11"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Comparison of dry conifer forest mapping: FIA vs. SAF vs. EVT


```{r table1, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
library(tidyverse)


options(knitr.kable.NA = '')
kbTable <- read_csv("data/kbTable.csv")

kbTable %>%
  kable("html",align = 'clc')%>%
  kable_styling(full_width = F,position="left",bootstrap_options = 
  c("striped","bordered"))
```

1 & 2 - Mapped core dry conifer forest types including grand fir, which could be present today on dry forest sites. Included a few minor dry conifer types (e.g. larch, incense cedar). Did not include oak/pine or juniper types.
3 - Mapped ponderosa pine, dry mixed conifer, and mesic mixed conifer types. Lumped regional variants to simplify display (e.g. Northern Rocky Mountains PIPO lumped w/ Southern Rocky Mountain PIPO)


## Pros and cons of each legend

```{r table2, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
library(tidyverse)


options(knitr.kable.NA = '')
kbTable2 <- read_csv("data/kbTable2.csv")

kbTable2 %>%
  kable("html",align = 'clc')%>%
  kable_styling(full_width = F,position="left",bootstrap_options = 
  c("striped","bordered"))
```

## Summary recommendation (Kori's thoughts)
* LF EVT has preferred legend for mapping dry conifer forest
* Better to lump EVTs into preferred types for mapping than to use LF SAF (retains integrity of original mapped classes vs. x-walk)
* FIA may be preferred for linking to literature and for C calculation but need to address issues w/ distinguishing dry vs. wet Douglas-fir and Mixed Conifer
* We could use LF EVT to split these out.

